%-------------------------
% Resume in Latex
% Author : Gu Junchao
% License : MIT, modified from Sourabh Bajaj's online template
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{http://franklingu.github.io/}{\Large Gu Junchao}}\\
  \href{https://franklingu.github.io/}{https://franklingu.github.io} & Email : \href{mailto:franklingujunchao@gmail.com}{franklingujunchao@gmail.com}\\
\end{tabular*}


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
  
    \resumeSubheading
      {PRO Unlimited @ Facebook}{Singapore}
      {Software Engineer}{Sept 2018 -- Present}
      \resumeItemListStart
        \resumeItem{Consumer Hardware Support Email Case}
          {Re-designed and implemented email case processing, resulting in great improvement in code maintainability and shortening response time by 10\%.}
        \resumeItem{Consumer Hardware Support App}
          {Migrated part of the web app to SPA for responsiveness and user-friendliness using React and React Router.}
      \resumeItemListEnd

    \resumeSubheading
      {Dynamic Technology Lab}{Singapore}
      {Data Engineer}{May 2016 -- Aug 2018}
      \resumeItemListStart
        \resumeItem{Data Manager}
          {Developed a project for managing data access for researchers, syncing data for users and monitoring data running status on many production machines, improving project collaboration among researchers, bringing up data research speed by 5\% and improving data monitor alarm accuracy by 30\%.}
        \resumeItem{Data Projects}
          {Worked with many researchers on various data projects by communicating with data vendors, developing solutions and cleaning up raw data, resulting in a gain of 10\% in research speed.}
      \resumeItemListEnd

    \resumeSubheading
      {Garena}{Singapore}
      {Web Developer (Internship)}{Jan 2016 -- Mar 2016}
      \resumeItemListStart
        \resumeItem{GPlus Admin}
          {Worked with 2 colleagues and developed an easy-to-use configuration admin panel for publishing game content on application and greatly enhanced the content management flow.}
        \resumeItem{Friends Notifier}
          {Designed and developed a system for notifying users when friends are online. Made use of Kafka to greatly improve scalability.}
      \resumeItemListEnd

    \resumeSubheading
      {NUS, School of Computing}{Singapore}
      {Teaching Assistant (Part-time)}{Aug 2014 -- Dec 2015}
      \resumeItemListStart
        \resumeItem{Coaching students}
          {Coached 2 teams of students per semester for a software engineering course and provided detailed and tailor-made feedback and explanation of knowledge about software development life cycle based on students’ ability, with improvement in knowledge of agile software development and communication effectiveness.}
      \resumeItemListEnd

    \resumeSubheading
      {Teammates @ Google Summer of Code}{Singapore}
      {Web Developer}{May 2014 -- Aug 2014} 
      \resumeItemListStart
        \resumeItem{Teammates}
        {Designed and developed access-control feature from ground up for Teammates system and finished the project two weeks ahead of deadline with expected quality and test coverage, resulting in a significant gain of experience with Java EE, jQuery and software development.}
        {Collaborated with 5 other project mates with mentoring from a senior lecturer in NUS, with a deeper understanding of project collaboration and GitHub flow as agile development.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {National University of Singapore}{Singapore}
      {Bachelor of Engineering in Computer Engineering;  CAP: 4.70/5.0)}{Aug. 2012 -- July. 2016}
      \resumeItemListStart
        \resumeItem{MOE Scholar}
          {Ministry of Education full scholarship}
        \resumeItem{Dean’s List in Faculty of Engineering}
          {Semester 1 of 2012/2013 \& Semester 2 of 2013/2014 \& Semester 1 of 2014/2015}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{comp-match}
      {Open source PyPI package for matching company name to underlines.}
    \resumeSubItem{NUSSkylab}
      {Open source application for NUS Orbital project for peer evaluations.}
    \resumeSubItem{VConcierge}
      {Hackathon project that won us first prize in DBS Hackathon.}
  \resumeSubHeadingListEnd


%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
  \resumeSubHeadingListStart
    \resumeSubItem{Languages}
    {Python (Proficient), JavaScript(Proficient), Hack (Proficient), Java (Familiar)}
    \resumeSubItem{Technologies}
    {Django (Proficient), Flask (Proficient), React.js (Proficient), Vue.js (Familiar)}
 \resumeSubHeadingListEnd

%--------HOBBIES------------
\section{Hobbies}
  \resumeSubHeadingListStart
    \resumeSubItem{Reading}
    {Enjoy conversations with authors and relax myself during reading.}
    \resumeSubItem{Badminton and swimming} 
    {Improve physical fitness. }
 \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
